Can we use reallocated logbooks data to map species distribution habitats?

### 2022-01-07 Version_M2_plusieurszones/draft/paper_3/paper_3.Rmd
paper_3

```{r setup, include = FALSE}
library("papaja")
```

@@

@@

How to justify the number of fishing sequence and the number of VMS pings?

@@

>>>>

```{r setup, include = FALSE}
library(cowplot)
library(doBy)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(kableExtra)
library(papaja)
```

@@

How many simulations? 100 or more?

@@

Still some lack of convergence.

Number of pings | nu:
1|10
10|100
100|1000

Size within a fishing sequence: radius = 3

Number of fishing zones: 1|3|5

@@

## Single square analysis

```{r}

load("res/Results_full_single_square.RData")

## Table of convergence
Results_conv <- Results
Results_conv$one <- 1
Results_conv_2 <- summaryBy(Convergence+one~
                              sequencesdepeche+
                              # zonespersequence+
                              aggreg_obs+
                              # b_true+
                              n_samp_com+
                              reallocation,
                            data=Results_conv,
                            FUN=sum) %>%
  dplyr::select(n_samp_com,
                sequencesdepeche,
                # zonespersequence,
                reallocation,
                aggreg_obs,
                Convergence.sum,
                one.sum) %>%
    mutate(aggreg_obs = ifelse(aggreg_obs == T,"Dj","Yi"),
           reallocation = ifelse(reallocation == 1,"Yes","No"),
           perc_convergence = round((1 - Convergence.sum / one.sum)*100,digits = 3))

Results_conv_2$n_samp_com <- as.integer(Results_conv_2$n_samp_com)
Results_conv_2$sequencesdepeche <- as.integer(Results_conv_2$sequencesdepeche)

Results_conv_2 <- Results_conv_2 %>%
  dplyr::rename(`Nb samples` = n_samp_com,
                `Fishing sequence` = sequencesdepeche,
                `Reallocation` = reallocation,
                `Likelihood level` = aggreg_obs,
                `Convergence (%)` = perc_convergence) %>%
  dplyr::select(-Convergence.sum,-one.sum)

knitr::kable(Results_conv_2,booktabs = T,align = "c",
                  caption = "Percentage of convergence per simulation/model configuration")

```

```{r}

## Plot Performance metric
Results <- Results %>%
  filter(b_true == 0 & Convergence == 0)
Results[,"RelBias_N"]=(Results[,"N_est"]-Results[,"N_true"])/Results[,"N_true"]
Results[,"RelBias_beta"]=(Results[,"beta1_est"]-Results[,"beta1_true"])/Results[,"beta1_true"]
Results[,"Bias_b"]=(Results[,"b_est"]-Results[,"b_true"]) / ifelse(Results[,"b_true"] != 0,Results[,"b_true"],1)

Results <- Results %>%
  mutate(relloc_aggreg = paste0("Reallocation: ",ifelse(reallocation==0,"No","Yes")," -  Likelihood: ",ifelse(aggreg_obs==T,"Dj","Yi")))

Results$zonespersequence <- as.factor(Results$zonespersequence)
Results$b_true <- as.factor(Results$b_true)
Results$relloc_aggreg <- factor(Results$relloc_aggreg,
                                levels = c("Reallocation: No -  Likelihood: Yi",
                                           "Reallocation: Yes -  Likelihood: Yi",
                                           "Reallocation: Yes -  Likelihood: Dj"))

Results_2 <- Results %>%
  filter(n_samp_com > 10)

RelBias_N_plot <- ggplot()+
  geom_boxplot(data = Results_2,
               aes(x = zonespersequence,
                   y = RelBias_N,
                   fill = relloc_aggreg))+
  geom_hline(yintercept = 0,linetype="dashed")+
  theme_bw()+
  ylab("Relative bias of biomass")+
  facet_wrap(.~factor(n_samp_com))+
  theme(legend.title = element_blank(),
        aspect.ratio = 1,
        legend.position = 'none')+
  ylim(-1,2)+
  ylab("")+xlab("")

RelBias_beta_plot <- ggplot()+
  geom_boxplot(data = Results_2,
               aes(x = zonespersequence,
                   y = RelBias_beta,
                   fill = relloc_aggreg))+
  geom_hline(yintercept = 0,linetype="dashed")+
  theme_bw()+
  ylab("Relative bias of beta1")+
  facet_wrap(.~factor(n_samp_com))+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1)+
  ylab("")+xlab("")

MSPE_S_plot <- ggplot()+
  geom_boxplot(data = Results_2,
               aes(x = zonespersequence,
                   y = log(MSPE_S),
                   fill = relloc_aggreg))+
  theme_bw()+
  # ylab("MSPE")+
  facet_wrap(.~factor(n_samp_com))+
  theme(legend.title = element_blank(),
        legend.position = "none",
        aspect.ratio = 1)+
  ylab("")+xlab("")

legend <- as_ggplot(cowplot::get_legend(MSPE_S_plot+theme(legend.position="right",legend.title = element_blank())))

Perf.metric <- plot_grid(RelBias_N_plot,
                      RelBias_beta_plot,
                      MSPE_S_plot,
                      legend,
                      ncol = 1,rel_heights = c(1,1,1,0.25))

ggsave("images/Perf.metric_single_square.png",width = 7.5/1.5, height = 15/1.5)

```

### 2022-01-07 Version_M2_plusieurszones/draft/paper_3/paper_3.tex
paper_3

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The title},
  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Title}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\title{The title}
\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
\date{}

@@

How to justify the number of fishing sequence and the number of VMS pings?

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Can we use reallocated logbooks data to map species distribution habitats?},
  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{SHORTTITLE}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\title{Can we use reallocated logbooks data to map species distribution habitats?}
\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
\date{}

@@

Still some lack of convergence.

Number of pings \textbar{} nu:
1\textbar10
10\textbar100
100\textbar1000

Size within a fishing sequence: radius = 3

Number of fishing zones: 1\textbar3\textbar5

@@

\hypertarget{single-square-analysis}{%
\subsection{Single square analysis}\label{single-square-analysis}}

\begin{table}

\caption{\label{tab:unnamed-chunk-1}Percentage of convergence for each simulation/model configuration}
\centering
\begin{tabular}[t]{ccccc}
\toprule
Nb samples & Fishing sequence & Reallocation & Likelihood level & Convergence (\%)\\
\midrule
10 & 1 & No & Yi & 99.668\\
10 & 1 & Yes & Yi & 0.333\\
10 & 1 & Yes & Dj & 0.000\\
100 & 10 & No & Yi & 100.000\\
100 & 10 & Yes & Yi & 100.000\\
\addlinespace
100 & 10 & Yes & Dj & 92.000\\
1000 & 100 & No & Yi & 100.000\\
1000 & 100 & Yes & Yi & 100.000\\
1000 & 100 & Yes & Dj & 97.333\\
\bottomrule
\end{tabular}
\end{table}
